---
title: "Exercise - Dates and times with Lubridate"
subtitle: "Live Session"
output: 
  html_document:
    toc: TRUE
    df_print: paged
    number_sections: FALSE
    highlight: tango
    theme: lumen
    toc_depth: 3
    toc_float: true
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

## Welcome!

In this session we are going to work with **DATES** and **TIMES** with the **LUBRIDATE** package!

Why do we need a package for that?

- Dates come in different forms and shapes:
  - 01.09.2022
  - 01/09/22
  - 09-01-2022
  - SEP-09-22
  - September, 09, 2022
  - 09 SEP 22
  
- Many details for dates and time:
  - Lead years
  - Daylight savings time (DST) 
  - Time zones

- For doing calculations with dates

## Load packages for this exercise ## 

```{r}

library(lubridate)
library(tidyverse)

```

## Date and time objects ## 

How do we find out today's date?

```{r}

today <- today()
today

```

How can we find out the current date and time?

```{r}

now <- now()
now

```

How do we create one date and one datetime to show 12:00 pm on the 1st of August 2015?

```{r}

date_1 <- "2015 08 01 12:00:00"

date_2 <- as_date(date_1)
date_2

datetime_3 <- ymd_hms(date_1)
datetime_3

```

How do we tell R these are dates? 

"1956 Jun 20"

```{r}

ymd("1956 JUN 20")

```


"14.07.2023"

```{r}

dmy("14.07.2023")

```

How do we tell R this has a date and time?

"14072003153000"

```{r}

dmy_hms("14072003153000")

```

## Extracting components for date and time ##

Extract the unabbreviated name of the month and the abbreviated day of the week for "14072003153000"

```{r}

extracted_date <- dmy_hms("14072003153000")

month(extracted_date, label = TRUE, abbr = FALSE)

wday(extracted_date, label = TRUE)

```
## FIFA World Cup 2022 ##

#### First load data for the FIFA World Cup 2022 matches

Convert the date column to datetime in R in the Qatar timezone. 
```{r}

FIFA <- read.csv("fifa-world-cup-2022-ArabStandardTime.csv")
#OlsonNames()

Extracted_dates <- dmy_hm(FIFA$Date, tz = "Asia/Qatar") 
Extracted_dates %>% head(3)

```

On what date is the final match taking place? 

```{r}

last_match <- max(Extracted_dates)
last_match

```

Provide a countdown to the final match from this moment (number of hours, days, etc.).

```{r}

now <- now()
countdown <- last_match - now
as.period(countdown)

```

At what time in Berlin will the final match take place?

```{r}

with_tz(last_match, tzone = "UTC")

```
