---
title: "Exercise - Dates and times with Lubridate"
subtitle: "Live Session"
output: 
  html_document:
    toc: TRUE
    df_print: paged
    number_sections: FALSE
    highlight: tango
    theme: lumen
    toc_depth: 3
    toc_float: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

## Welcome!

In this session we are going to work with **DATES** and **TIMES** with the **LUBRIDATE** package!

Why do we need a package for that?

- Dates come in different forms and shapes:
  - 01.09.2022
  - 01/09/22
  - 09-01-2022
  - SEP-09-22
  - September, 09, 2022
  - 09 SEP 22
  
- Many details for dates and time:
  - Lead years
  - Daylight savings time (DST) 
  - Time zones

- For doing calculations with dates

## Load packages for this exercise ## 

```{r}

library(lubridate)
library(tidyverse)

```

## Date and time objects ## 

How do we find out today's date?
```{r}


```

How can we find out the current date and time?
```{r}


```

How do we create one date and one datetime to show 12:00 pm on the 1st of August 2015?

```{r}


```

How do we tell R these are dates? 

"1956 Jun 20"
```{r}



```

"14.07.2023"
```{r}



```
How do we tell R this has a date and time?

"14072003153000"
```{r}



```

## Extracting components for date and time ##

Extract the unabbreviated name of the month and the abbreviated day of the week for "14072003153000"

```{r}


```

## FIFA World Cup 2022 ##

#### First load data for the FIFA World Cup 2022 matches

Convert the date column to datetime in R in the Qatar timezone. 
```{r}


```

On what date is the final match taking place? 

```{r}


```

Provide a countdown to the final match from this moment (number of hours, days, etc.).

```{r}



```

At what time in Berlin will the final match take place?

```{r}



```
